Energy and the CES production function

### 2015-09-02 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed line order on historical graphs.

  mutate( 
    # Change variable names to make a nicer-looking graph and relevel factors before plotting
    variable = plyr::mapvalues(variable,
                               from=c("iGDP", 
                                      "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
                                      "iL", "ihLest",
                                      "iXpMP", "iXp", "iUMP", "iU"),
                               to=c("y", 
                                    "k", "k", "k", "k",
                                    "l", "l",
                                    "e", "e", "e", "e")),
    Country = relevelFactor(factor(Country), c("PT", "UK")), # Adjusts facet order
    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")) # Adjusts facet order
  )

historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  facet_formula = flavor ~ Country, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
xlab("") + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
ylab("Indexed (1960=1)") +
scale_fill_discrete(breaks=c("y", "k", "l", "e"))
@

>>>>

  mutate( 
    # Change variable names to make a nicer-looking graph and relevel factors before plotting
    variable = plyr::mapvalues(variable,
                               from=c("iGDP", 
                                      "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
                                      "iL", "ihLest",
                                      "iXpMP", "iXp", "iUMP", "iU"),
                               to=c("y", 
                                    "k", "k", "k", "k",
                                    "l", "l",
                                    "e", "e", "e", "e")),
    Country = relevelFactor(factor(Country), c("PT", "UK")), # Adjusts facet order
    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")), # Adjusts facet order
    variable = relevelFactor(factor(variable), c("y", "k", "l", "e"))
  )

historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  facet_formula = flavor ~ Country, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
xlab("") + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
ylab("Indexed (1960=1)")
@
